---
title: "MigParl - Making of"
author: "Christoph Leonhardt"
date: "03 November 2019"
output: html_document
bibliography: migpress.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

# Making of MigParl (post-beta) 

`MigParl` is a corpus of plenary debates about migration and integration in the German federal states. It was first presented during a workshop of the MigTex project in November 2018 as a beta version with limited access to the participants of the event. Since then, the corpus has seen major improvements. The following document serves as a technical documentation of this development. It is divided into four subsections: 1) Dictionary-Based topic selection, 2) The encoding of topic probabilities, 3) the creation of subcorpora from the initial corpora containing all speeches according to these probabilities, 4) The creation of subcorpora according to another dictionary approach following the reasoning presented in the documentation of `MigPress`, 5) the actual decoding of the identified speeches and 6) the merge and reencoding of these subcorpora to create `MigParl`.

<!-- 

This document can be rendered from the console. This only will work if both the speech and the migration_integration_probability s-Attribute is already annotated and encoded in the corpora. For this, document 02 has to be executed by hand earlier.

```{r, echo = FALSE, eval = FALSE}
Rscript -e 'rmarkdown::render(input = "MigParl_Making-of.Rmd", output_format = "html_document", output_file = "MigParl_Making-of.html")'
```

--> 


```{r, echo = FALSE, eval = FALSE}
rmd <- list.files(pattern = '*.Rmd', recursive = T)
chunks <- paste0("```{r child = '", rmd, "'}\n```\n")
cat(chunks, sep = '\n')

starttime <- Sys.time()
```


```{r child = '01_Topic_Selection_By_Dictionary.Rmd'}
```

```{r child = '02_Encode_Speeches_and_Topic_Probabilities.Rmd'}
```

```{r child = '03_Subset_Corpora_By_Migration_and_Integration_Probability.Rmd'}
```

```{r child = '04_Subset_Corpus_Based_On_MigPress_Dictionary.Rmd'}
```

```{r child = '05_Decode_Token_Streams.Rmd'}
```

```{r child = '06_Reencode_Token_Streams_To_CWB.Rmd'}
```

```{r echo = FALSE}
Sys.time() - starttime
```

# SessionInfo

```{r sessioninfo, echo = FALSE}
sessionInfo()
```

# References
