---
title: "MigParl Corpus Data Report"
date: "`r Sys.Date()`"
output: html_document
params:
  target: "MIGPARL"
  package_to_use: "MigParl"
  print_out: TRUE
---

## Introduction

This document is parametrized and can be generated from the command line, passing the corpus to report on as a parameter, as follows.

```{sh command_line_use, eval = FALSE}
Rscript -e 'rmarkdown::render(input = "data_report_template.Rmd", output_format = "html_document", output_file = "data_report_be.html", params = list(target = "MIGPARL", print_out = "TRUE"))'
```

```{r echo = FALSE}
print_out <- params$print_out
```


## Getting Started

```{r}
library(data.table)
```

```{r, echo = FALSE}
target <- params$target
package_to_use <- params$package_to_use
get_corpus_build_date <- function(package, corpus) {
  firstline <- readLines(paste0(system.file(package = package, "extdata", "cwb", "indexed_corpora", tolower(corpus)), "/info.md"))[1]
  date <- gsub(".*build (.*?)\\)", "\\1", firstline)
  date <- as.Date(date)
  return(date)
}

corpus_build_date <- get_corpus_build_date(package = package_to_use, corpus = target)

target <- params$target
print(sprintf("This is a data report for the %s corpus (corpus build date: %s)", target, corpus_build_date))
```


```{r}
library(polmineR)
use("MigParl")
if (!target %in% corpus()[["corpus"]]){
  MigParl::migparl_download_corpus(target)
  use("MigParl")
}
```


## Structural and Positional Attributes

```{r}
p_attributes(target)
```

```{r}
s_attributes(target)
```


The size of the entire corpus is about `r format(round(size(target) / 1e6, 2), trim = TRUE)` million tokens. 


## Report on Structural Attributes

### Structural Attribute "date" (and year)

```{r}
dates <- s_attributes(target, "date")
dates <- as.Date(dates)
table(is.na(dates))
min(dates)
max(dates)
```

The corpus covers the time span between `r min(dates, na.rm = TRUE)` and `r max(dates, na.rm = TRUE)`. There are `r length(which(is.na(dates) == TRUE))` missing values in the date attributes.


```{r}
dt_date <- size(target, s_attribute = "date")
dt_date[, "date" := as.Date(dt_date[["date"]])]
setorderv(dt_date, "date")
DT::datatable(dt_date)
```

```{r}
dt_date[, "year" := format(dt_date[["date"]], "%Y")]
dt_year <- dt_date[, sum(.SD[["size"]]), by = "year"]
setnames(dt_year, old = "V1", new = "size")
DT::datatable(dt_year)
```

```{r}
barplot(
  height = dt_year[["size"]]/1000000,
  names.arg = dt_year[["year"]],
  las = 2,
  main = sprintf("Tokens per Year in Million ", target)
  )
```

```{r eval = print_out, echo = FALSE, fig.show = FALSE}
library(ggplot2)
ggplot(dt_year, aes(year, size)) +
  geom_col(fill = "steelblue4") +
  theme_minimal() + 
  scale_y_continuous(labels = scales::number) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        text = element_text(family = "Microsoft Sans Serif"),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)) 
        ) +
  labs(title = "MigParl-Korpus - Jahr", 
       x = "Jahr", 
       y = "Größe in Token", 
       caption = sprintf("Korpusversion: %s", corpus_build_date))

ggsave("img/year_dt.jpeg", device = "jpeg")
```


### Structural Attribute "calendar_week"

```{r eval = print_out, echo = FALSE, fig.show = FALSE}
size_calendar_week <- size("MIGPARL", "calendar_week")

# sets the date of the thursday of the week as date 
# https://stackoverflow.com/questions/45549449/transform-year-week-to-date-object/45587644#45587644
size_calendar_week$week_as_date <- ISOweek::ISOweek2date(
  gsub("(\\d{4}-)(\\d{2}).*?", "\\1W\\2-4", size_calendar_week$calendar_week)
)

ggplot(size_calendar_week, aes(week_as_date, size)) +
  geom_col(fill = "steelblue4") +
  theme_minimal() + 
  scale_y_continuous(labels = scales::number) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        text = element_text(family = "Microsoft Sans Serif"),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)) 
  ) +
  labs(title = "MigParl-Korpus - Kalenderwochen", 
       x = "Kalenderwoche", 
       y = "Größe in Token", 
       caption = sprintf("Korpusversion: %s", corpus_build_date)
       ) +
  scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 year")

ggsave("img/calendar_week_dt.jpeg", device = "jpeg")
```


### Structural Attribute "party"

```{r}
DT::datatable(as.data.frame(size(target, s_attribute = "party")))
```

```{r eval = print_out, echo = FALSE,  fig.show = FALSE}
dt_party <- size(target, s_attribute = "party")
dt_party_min <- dt_party[which(dt_party$size > 100000),]

ggplot(dt_party_min, aes(reorder(party, -size), size)) +
  geom_col(fill = "steelblue4") +
  theme_minimal() + 
  scale_y_continuous(labels = scales::number) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        text = element_text(family = "Microsoft Sans Serif"),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)) 
        ) +
  labs(title = "MigParl-Korpus - Parteien", 
       subtitle = "Parteien mit mehr als 100.000 Token",
       x = "Partei", 
       y = "Größe in Token", 
       caption = sprintf("Korpusversion: %s", corpus_build_date))

ggsave("img/dt_party.jpeg", device = "jpeg")
```


### Structural Attribute "role"

```{r}
dt_role <- size(target, s_attribute = "role")
DT::datatable(dt_role)
```

```{r eval = print_out, echo = FALSE,  fig.show = FALSE}
dt_role <- size(target, s_attribute = "role")

ggplot(dt_role, aes(reorder(role, -size), size)) +
  geom_col(fill = "steelblue4") +
  theme_minimal() + 
  scale_y_continuous(labels = scales::number) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        text = element_text(family = "Microsoft Sans Serif"),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)) 
        ) +
  labs(title = "MigParl-Korpus - Rollenvergleich", 
       x = "Rolle", 
       y = "Größe in Token", 
       caption = sprintf("Korpusversion: %s", corpus_build_date))

ggsave("img/dt_role.jpeg", device = "jpeg")
```


### Structural Attribute "speaker"

```{r}
DT::datatable(size(target, s_attribute = "speaker"))
```


### Structural Attribute "regional_state"

```{r}
rs_dt <- size(target, s_attribute = "regional_state")
DT::datatable(rs_dt)
```

```{r}
barplot(
  height = rs_dt[["size"]],
  names.arg = rs_dt[["regional_state"]],
  las = 2,
  main = sprintf("Token per regional state (%s)", target)
  )
```

```{r eval = print_out, echo = FALSE,  fig.show = FALSE}
ggplot(rs_dt, aes(reorder(regional_state, -size), size)) +
  geom_col(fill = "steelblue4") +
  theme_minimal() + 
  scale_y_continuous(labels = scales::number) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        text = element_text(family = "Microsoft Sans Serif"),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)) 
        ) +
  labs(title = "MigParl-Korpus - Bundesländer", 
       x = "Bundesland", 
       y = "Größe in Token", 
       caption = sprintf("Korpusversion: %s", corpus_build_date))

ggsave("img/rs_dt.jpeg", device = "jpeg")
```



### Structural Attribute "dict_source" and "dict_topic_model"

Speeches are sampled with two different approaches which are described in detail in other parts of the `MigParl` documentation. Here, the consequences of these different sampling techniques should be illustrated in one graph. The year overview shown earlier is appended to account for the origin of the speech. 

```{r echo = FALSE,  fig.show = FALSE}
x <- size("MIGPARL", c("year", "source_dict", "source_topic_model"))
x$`Samplingstrategie` <- ifelse(x$source_dict == TRUE & x$source_topic_model == TRUE, "Beide Ansätze", ifelse(x$source_dict == TRUE & x$source_topic_model == FALSE, "Diktionär", "Topic Model"))

x$source_dict <- NULL
x$source_topic_model <- NULL

ggplot(x, aes(year, size, fill = factor(Samplingstrategie, levels=c("Diktionär", "Topic Model", "Beide Ansätze")))) +
  geom_col() +
  theme_minimal() + 
  scale_y_continuous(labels = scales::number) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        text = element_text(family = "Microsoft Sans Serif"),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        legend.position = c(.06, .95),
        legend.justification = c("left", "top"),
        legend.box.just = "left",
        legend.margin = margin(6, 6, 6, 6), 
        legend.box.background = element_rect()
  ) +
  labs(title = "MigParl-Korpus im Jahresverlauf", 
       subtitle = "Gestaptelt nach Samplingstrategie mit der eine Rede als relevant identifiziert wurde",
       x = "Jahr", 
       y = "Größe in Token", 
       caption = sprintf("Korpusversion: %s", corpus_build_date)) +
  scale_fill_manual(name = "Samplingstrategie", values = c("#77BCA9", "#F78E1E", "#015077"))

ggsave("img/dt_year_source.jpeg", device = "jpeg")
```



### Print one sample speech

```{r, message = FALSE, echo = FALSE, results="asis"}
random_year <- sample(s_attributes(target, "year"), 1)
mp_partition <- partition(target, year = random_year, role = "mp")
sample_day <- sample(s_attributes(mp_partition, "date"), size = 1)
sample_partition <- partition(mp_partition, date = sample_day)
speeches <- as.speeches(sample_partition, s_attribute_name = "speaker")
read(speeches[[1]], meta = c("speaker", "party", "date", "lp", "session", "regional_state", "source_dict", "source_topic_model"), cutoff = 10000)
```
